### 2019-05-03 monograph/thesis/chapters/conclusion.tex
Moved bad placed text from introduction to conclusion.tex and
removed the drafts from conclusion.tex to draft_for_implementation.tex

\cleardoublepage
\phantomsection %The \phantomsection command is needed to create a link to a place in the document that is not a figure, equation, table, section, subsection, chapter, etc.
\addcontentsline{toc}{chapter}{\texorpdfstring{\MakeTextUppercase{Capítulo 3}}{Capítulo 3}}

\chapter{Lorem ipsum dolor sit amet}

\begin{flushright}
    \showfont
\end{flushright}

\newpage

% ---
\section{Aliquam vestibulum fringilla lorem}
% ---

Lipsum me [1]

Lipsum me [2-3]

>>>>

% The \phantomsection command is needed to create a link to a place in the document that is not a
% figure, equation, table, section, subsection, chapter, etc.
%
% When do I need to invoke \phantomsection?
% https://tex.stackexchange.com/questions/44088/when-do-i-need-to-invoke-phantomsection
\phantomsection

% ---
% Conclusão (outro exemplo de capítulo sem numeração e presente no sumário)
% ---
\chapter[]{\lang{Conclusion}{Conclusão}}

\lang{%
    The difference from this proposal to remaining formatting tools,
    is the tradeoff between end\hyp{}users and developers responsibilities.
    Most tools rarely expose to end\hyp{}users their language syntax specification,
    in contrast,
    this proposal completely exposes the language to the end\hyp{}user as simple plain\hyp{}text,
    not requiring the tool to know any language syntax neither semantics.
    Moreover,
    with no syntax knowledge required,
    the tool be can used with any languages their user wishes to.
}{%

}

\begin{enumerate}[leftmargin=*]
    \item
        There are many different tools, sometimes paid, and difficult to
        complete. \cite{universalCodeFormatter}
    \item
        Many programming languages exist, so always having Beautifier
        software for each of them is very laborious
        \cite{universalCodeFormatter}. But the approach to a Universal
        Beautifier proposed in this work, would allow easily new languages to be
        added, being completely different from previous ones, or alike. And in
        case of similarities between them, it is enough to reuse their
        configuration structures already implemented.
    \item
        Looking for a Beautifier for each one of them because programmers
        currently work daily with several of these languages, and they are not
        similar. So you need to configure several beautifiers to do the
        formatting. This is a problem because only a few beautifiers are more
        complete, and every time you need to make a change in the formatting
        style, you must manually propagate the same change over several
        different program configuration files, which is bad because it takes the
        user a lot of time to learn how to handle many different types of
        settings. \cite{Schweitzer}
    \item
        In the case of ideal Beautifier, a change in your styling is
        propagated to all languages. And if you want to leave some language out
        of it, you just need to remove it from the list on which the
        configuration block applies to, and `a)' leave it out so no change is
        applied to. Or `b)' create a new block including only the block within
        the desired settings.
\end{enumerate}

### 2019-05-03 monograph/thesis/chapters/draft_for_implementation.tex
Moved bad placed text from introduction to conclusion.tex and
removed the drafts from conclusion.tex to draft_for_implementation.tex

>>>>

1.2      Rascunho da Monografia para TCC1

1.2.1    * Introdução       Uma breve descrição dos objetivos e da
           justificativa para realização do projeto. Uma breve explicação de
           qual a necessidade e importância deste projeto no escopo da
           Ciência da Computação. Os objetivo gerais e específicos buscados
           após a conclusão e análise deste projeto.

1.2.2    * Bibliográfia     Fazer uma análise do estado da arte em relação
         ao que existe hoje em dia de cunho científico, comentando sobre os
         diversos trabalhos na área de beautifying.

1.2.3    * Classificações   Escrever sobre quais são os tipos possíveis de
         beautifying. Quais são as técnicas mais eficientes, para quais
         linguagens ele se aplicam.

Cronograma:

Id      Atividade                               Data início    Data fim
1.2.2.a Escrever sobre os Formatadores Atuais   31/07/2017     30/08/2017
1.2.2.b Escrever sobre as Pesquisas Atuais      01/09/2017     15/09/2017
1.2.3.a Escrever as Classes de Beautifying      16/09/2017     30/09/2017
1.2.3.b Escrever os Tipos de Beautifying        01/10/2017     30/10/2017
1.2.4.a Fazer a Revisão do Texto Escrito        31/10/2017     20/11/2017

Coloca ChannelManager no tópico e boas praticas, e comenta sobre o modelo de
fork e canais.

Inclui a IA para reconhecer o formatação nos módulos de beautifying. Ela eh
uma heurística, que cada bloco implementa e faz ele gerar um arquivo de
configuração que representa a atual formatação do código (aqui esta o
verdadeiro desafio do trabalho, pesquise trabalhos correlatos).

Inclui sobre a implementação  do semantic linefeed implementado na seção do
linefeed.

Somente incluí somente o que é mais importante para entender o trabalho, não
queira mostrar tudo o que você fez. Uma trabalho extensivo não é necessário,
basta somente apontar como uma referencia que inclua o que você fez.

Mas não esqueça de incluir como foi implementado, i.e., os diagramas UML, se
o sistema é extensível, as bibliotecas utilizadas, como os testes foram
feitos e os resultados deles.

Coloca no capítulo de motivação a seção de trabalhos relacionados. Trabalhos
relacionados com beautifying e com as boas práticas de programação (code clean,
GOF, DEITEL (forminhas das boas práticas)). E deixa claro qual é o problema
que se está resolvendo.

Cria uma capitulo de comparação com os trabalhos relacionados, tanto a parte
teórica (boas práticas), quanto a parte prática (beautifier). Complexidade do
algoritmo do beautifier e o que esse trabalho tem de diferente dos outros.

Coloque evidencias de que funciona o formatador, de boas práticas, mas
práticas e críticas.

Fazer um texto mais didático com exemplos, para os leitores leigos.

recebi alguns comentários dos professores da banca sobre o seu TCC que
gostaria de repassar para voce.

Os dois professores se manifestaram a respeito da formatação que voce
usou. Como eu já havia comentado com voce, eles pedem que voce adote o
formato oficial da BU quando fizer o texto do TCC II no semestre que
vem, pois isso é obrigatório.

Reconhecem o mérito de voce fazer o texto em ingles mas comentam
também sobre a necessidade de fazer uma boa revisão no texto para
corrigir erros gramaticais. Talvez fosse o caso de voce buscar algum
profissional para isso, na versão final do texto

Quanto a estrutura, pedem que voce seja mais claro e conciso nos
objetivos específicos do tcc (há duas seções de objetivos) e o texto
está mais com estilo de um tutorial do que de um TCC.

No resumo, o objetivo também fica dúbio. Diz que vai estudar e depois
também propor uma linguagem. Acho que se a ideia é propor algo, focar
nisso e o resto é para apoio e suporte para fins de comparação

A revisão de literatura está um tanto confusa. Na seção da proposta
tem algumas partes que deveriam estar na fundamentação.

De minha parte, eu concordo com as observações e vamos agora trabalhar
em melhorar a organização do texto. Mas é importante que voce
transcreva o texto para o template da BU.

### 2019-05-03 monograph/thesis/chapters/introduction.tex
Moved bad placed text from introduction to conclusion.tex and
removed the drafts from conclusion.tex to draft_for_implementation.tex

\lang{%
    The work first part will be based on research in
    articles, books, theses, dissertations, trusted authors websites,
    and through new demonstrated evidences based on arguments
    in the monograph evolution.
    Also, present results after building a new tool
    which proposes a solution for the problems presented and detailed.
}{%
    A \hyperref[sec:primeira_parte]{primeira parte} deste trabalho será baseado em artigos,
    livros, outras dissertações,
    sites confiáveis e por novas evidências demonstradas no desenvolvimento deste trabalho.
}

\lang{%
    In this proposal last chapter which lies on the part
    called `\nameref{sec:segunda_parte}', which holds the implementation of a
    tool for code `Beautifying'.
}{%
    E finalmente,
    na \hyperref[sec:segunda_parte]{segunda parte} deste trabalho,
    será apresentada a sugestão e implementação de uma ferramenta.
}

\lang{%
    The difference from this proposal to remaining formatting tools,
    is the tradeoff between end\hyp{}users and developers responsibilities.
    Most tools rarely expose to end\hyp{}users their language syntax specification,
    in contrast,
    this proposal completely exposes the language to the end\hyp{}user as simple plain\hyp{}text,
    not requiring the tool to know any language syntax neither semantics.
    Moreover,
    with no syntax knowledge required,
    the tool be can used with any languages their user wishes to.
}{%

}

\begin{enumerate}[leftmargin=*]
    \item
        There are many different tools, sometimes paid, and difficult to
        complete. \cite{universalCodeFormatter}
    \item
        Many programming languages exist, so always having Beautifier
        software for each of them is very laborious
        \cite{universalCodeFormatter}. But the approach to a Universal
        Beautifier proposed in this work, would allow easily new languages to be
        added, being completely different from previous ones, or alike. And in
        case of similarities between them, it is enough to reuse their
        configuration structures already implemented.
    \item
        Looking for a Beautifier for each one of them because programmers
        currently work daily with several of these languages, and they are not
        similar. So you need to configure several beautifiers to do the
        formatting. This is a problem because only a few beautifiers are more
        complete, and every time you need to make a change in the formatting
        style, you must manually propagate the same change over several
        different program configuration files, which is bad because it takes the
        user a lot of time to learn how to handle many different types of
        settings. \cite{Schweitzer}
    \item
        In the case of ideal Beautifier, a change in your styling is
        propagated to all languages. And if you want to leave some language out
        of it, you just need to remove it from the list on which the
        configuration block applies to, and `a)' leave it out so no change is
        applied to. Or `b)' create a new block including only the block within
        the desired settings.
\end{enumerate}

>>>>

\lang{%
    The work first part will be based on research in
    articles, books, theses, dissertations, trusted authors websites,
    and through new demonstrated evidences based on arguments
    in the monograph evolution.
    Also, present results after building a new tool
    which proposes a solution for the problems presented and detailed.
}{%
    A \hyperref[sec:primeira_parte]{primeira parte} deste trabalho será baseado em artigos,
    livros, outras dissertações,
    sites confiáveis e por novas evidências demonstradas no desenvolvimento deste trabalho.
}%
\lang{%
    In this proposal last chapter which lies on the part
    called `\nameref{sec:segunda_parte}', which holds the implementation of a
    tool for code `Beautifying'.
}{%
    E finalmente,
    na \hyperref[sec:segunda_parte]{segunda parte} deste trabalho,
    será apresentada a sugestão e implementação de uma ferramenta.
}
